---
title: "Comparable Regression Analysis 4"
author: "Tongfang Sun"
date: "August 5, 2016"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

From the presivous analysis result, we try to find the pure relation between colorfullness/complexity and rating without considering user's gender, age, education' effects towards to model. Thus, we will regroup the dataset and then do the fitted linear regression model. Except, that, we will choose some web imgs as compare test after the model is finished. The imgs are eng(346, 347, 348, 349), webby(18, 19). grayscale(18, 19)...

```{r dataset_format}
library(ggplot2)
train_dat <-  read.table("/Volumes/STF/Final_siemens/Research_Qi/Test4/train_list_color_complx.txt", quote="\"")
test_dat <- read.table("/Volumes/STF/Final_siemens/Research_Qi/Test4/test_list_color_complx.txt", quote="\"")

web <- c(train_dat$V1)
rate <- c(train_dat$V2)
color <- c(train_dat$V3)
compl <- c(train_dat$V4)
dat_tarin <- data.frame(rate, color, compl)
# analysis rate itself
par(mfrow=c(1, 2))
qqnorm(rate)
qqline(rate, col = 2)

hist(rate)
hist((compl)^0.4)

hist(color)

hist(color^0.4)

#qqnorm(rate, color)
par(mfrow=c(1, 2))
qqplot(color, rate, xlab = "colorfullness", ylab = "mean rate value")
qqplot(compl, rate, xlab = "complextymodel", ylab = "mean rate value")



# Individual Pearson correlation (rate, colorfulness, complexity)
df <- data.frame(rate, color, compl)
plot(df[,1:3])
cor(df[, 1:3], method = "pearson")
```

Normal Linear Regression (colorfulness + complexity)
``` {r linear_regression_model}
lm1 <- lm(rate ~ color + compl)
summary(lm1)
anova(lm1)
# Pearsonn's correlation (compare itself)
par(mfrow=c(1, 1))
resid.nlm <- resid(lm1)
plot(resid.nlm + rate, rate, ylab = "real rate", xlab = "nlm.model estimate")
cor.test(resid.nlm+rate, rate)

## Test
rate <- test_dat$V2
color <- test_dat$V3
compl <- test_dat$V4
cnn <- test_dat$V5

mytest <- data.frame(rate, color, compl)
estimate <- predict(lm1 , newdata = mytest, se.fit = TRUE, interval = "prediction")
predi_value <- estimate$fit[,1]

par(mfrow=c(1, 2))
qqplot(color, rate)
qqplot(compl, rate)

mytest <- data.frame(rate, color, compl, cnn)
estimate <- predict(lm1 , newdata = mytest)

predi_value <- estimate
par(mfrow=c(1, 1))
cor.test(mytest$rate, predi_value)
```


Linear + Interaction
``` {r linearn_model}
lm1 <- lm(rate ~  color +  compl + color * compl)
summary(lm1)
anova(lm1)
# Pearsonn's correlation (compare itself)
par(mfrow=c(1, 1))
resid.nlm <- resid(lm1)
plot(resid.nlm + rate, rate, ylab = "real rate", xlab = "nlm.model estimate")
cor.test(resid.nlm+rate, rate)

## Test
rate <- test_dat$V2
color <- test_dat$V3
compl <- test_dat$V4
cnn <- test_dat$V5

mytest <- data.frame(rate, color, compl)
estimate <- predict(lm1 , newdata = mytest, se.fit = TRUE, interval = "prediction")
predi_value <- estimate$fit[,1]

par(mfrow=c(1, 2))
qqplot(color, rate)
qqplot(compl, rate)

mytest <- data.frame(rate, color, compl, cnn)
estimate <- predict(lm1 , newdata = mytest)

predi_value <- estimate
par(mfrow=c(1, 1))
cor.test(mytest$rate, predi_value)
```



Linear + Interaction color reduce
``` {r linear_regression_model2}
lm1 <- lm(rate ~  compl + color * compl)
summary(lm1)
anova(lm1)
# Pearsonn's correlation (compare itself)
par(mfrow=c(1, 1))
resid.nlm <- resid(lm1)
plot(resid.nlm + rate, rate, ylab = "real rate", xlab = "nlm.model estimate")
cor.test(resid.nlm+rate, rate)

## Test
rate <- test_dat$V2
color <- test_dat$V3
compl <- test_dat$V4
cnn <- test_dat$V5

mytest <- data.frame(rate, color, compl)
estimate <- predict(lm1 , newdata = mytest, se.fit = TRUE, interval = "prediction")
predi_value <- estimate$fit[,1]

par(mfrow=c(1, 2))
qqplot(color, rate)
qqplot(compl, rate)

mytest <- data.frame(rate, color, compl, cnn)
estimate <- predict(lm1 , newdata = mytest)

predi_value <- estimate
par(mfrow=c(1, 1))
cor.test(mytest$rate, predi_value)
```


Original 5 factor + interaction 0.62

``` {r 3}
lm1 <- lm(rate ~ color + compl + I(color^(exp(1))) + I(compl^(0.4)) + I(abs(color^3 - compl^3)) + color * compl)

summary(lm1)
anova(lm1)
# Pearsonn's correlation (compare itself)
par(mfrow=c(1, 1))
resid.nlm <- resid(lm1)
plot(resid.nlm + rate, rate, ylab = "real rate", xlab = "nlm.model estimate")
cor.test(resid.nlm+rate, rate)

## Test
rate <- test_dat$V2
color <- test_dat$V3
compl <- test_dat$V4
cnn <- test_dat$V5

mytest <- data.frame(rate, color, compl)
estimate <- predict(lm1 , newdata = mytest, se.fit = TRUE, interval = "prediction")
predi_value <- estimate$fit[,1]

par(mfrow=c(1, 2))
qqplot(color, rate)
qqplot(compl, rate)

mytest <- data.frame(rate, color, compl, cnn)
estimate <- predict(lm1 , newdata = mytest)

predi_value <- estimate
par(mfrow=c(1, 1))
cor.test(mytest$rate, predi_value)
```




According to QQplot result, the colorfulness and complexity should fit the mean rate value by normal distribution approximately. Thus, We will try two different regression model to see the result: normal linear regression model and fitted linear regression model

```{r regression_model}

n.lm <- lm(rate ~ color + compl + I(color^(exp(1))) + I(compl^(0.4)) + I(abs(color^3 - compl^3)))
summary(n.lm)
anova(n.lm)
par(mfrow=c(2,2))                 
plot(n.lm)


# Pearsonn's correlation (compare itself)
par(mfrow=c(1, 1))
resid.nlm <- resid(n.lm)
plot(resid.nlm + rate, rate, ylab = "real rate", xlab = "nlm.model estimate")
cor.test(resid.nlm+rate, rate)


```


After finish the model, we then use test_list_color_complx.txt to test the model

```{r test}

rate <- test_dat$V2
color <- test_dat$V3
compl <- test_dat$V4
cnn <- test_dat$V5

# color2 = color
# 
# for (i in 1:length(color)) {
#      if(color[i] < 3.5) {
#       color2[i] = color[i] * 0.8
#     } else if (color[i] > 7) {
#       color2[i] = color[i] * 1.8
#     } else {
#       color2[i] = color[i]
#     }
# }
# 

mytest <- data.frame(rate, color, compl)

estimate <- predict(n.lm , newdata = mytest, se.fit = TRUE, interval = "prediction")
predi_value <- estimate$fit[,1]

par(mfrow=c(1, 2))
qqplot(color, rate)
qqplot(compl, rate)


mytest <- data.frame(rate, color, compl, cnn)
estimate <- predict(n.lm , newdata = mytest)

predi_value <- estimate
par(mfrow=c(1, 1))
cor.test(mytest$rate, predi_value)

final_data <- data.frame(test_dat, predi_value)

```


After the linear model is done, we will compare the test result with CNN test result and real rate using  Person table.

```{r compare}
compare_table <- data.frame(mytest$rate, test_dat$V5, predi_value)
hist(mytest$rate)
plot(compare_table[,1:3])
cor(compare_table[, 1:3], method = "pearson")


# CNN predict
plot(test_dat$V5, mytest$rate, xlim=c(2, 7), ylim=c(2, 7), ylab = "Real Rate", xlab = "CNN predict rate")



p1 <- ggplot(test_dat, aes(x = test_dat$V2, y = test_dat$V5)) + geom_point(colour = "#48b9f3", size = 3, alpha = 1)
 
p1 + geom_smooth(method = lm, se = FALSE) + labs(x = "User Aesthetics Rating", y = "CNN Predict Rating") + xlim(2.2, 6.5) + ylim(2.2, 6.5) + theme_bw()


# linear regression
plot(predi_value, mytest$rate, xlim=c(2, 7), ylim=c(2, 7), ylab = "Real Rate", xlab = "regression predict rate")

new_dat <- data.frame(test_dat, predi_value)
p2 <- ggplot(new_dat, aes(x = new_dat$V2, y = predi_value)) + geom_point(colour = "#48b9f3", size = 3, alpha = 1)
p2 + geom_smooth(method = lm, se = FALSE) + labs(x = "User Aesthetics Rating", y = "Linear Predict Rating") + xlim(2.2, 6.5) + ylim(2.2, 6.5) + theme_bw()


# linear regression vs cnn
plot(predi_value, test_dat$V5 , xlim=c(2, 7), ylim=c(2, 7), ylab = "CNN predict rate", xlab = "regression predict 
rate")

true_rate = new_dat$V2
cnn_rate = new_dat$V5
linear_rate = predi_value



dat <- data.frame(xx =c(true_rate, cnn_rate, linear_rate), yy = rep(letters[1:3], each = length(cnn_rate)))


## Histogram user aesthetics rating
p4 <- ggplot(dat, aes(x = xx)) +
  geom_histogram(data = subset(dat, yy == 'a'), aes(y = ..density..), binwidth=.6, colour="black", fill = "white", alpha = 0.5) + 
  geom_density(data = subset(dat, yy == 'a'), fill = "#f7746c", colour = "#f7746c", alpha = 0.2) + xlim(1, 8)
p4 + theme_bw() 


## Histogram cnn predict rating
p6 <- ggplot(dat, aes(x = xx)) +
  geom_histogram(data = subset(dat, yy == 'b'), aes(y = ..density..), binwidth =.8, colour="black", fill = "white", alpha = 0.5) + 
  geom_density(data = subset(dat, yy == 'b'), colour = "#05bdc2", fill = "#05bdc2", alpha = 0.2) + xlim(1, 8)
  
p6 + theme_bw() 


p7 <- ggplot(dat, aes(x = xx)) +
   geom_histogram(data = subset(dat, yy == 'a'), aes(y = ..density..), fill = "#f7746c", alpha = 0.5) +
  geom_histogram(data = subset(dat, yy == 'b'), aes(y = ..density..), fill = "#05bdc2", alpha = 1) 
  
  p7 + theme_bw() 
  
# p4 + stat_function(fun = dnorm, args = list(mean = mean(cnn_rate), sd = sd(cnn_rate)), lwd = 2, color = "red")


p5 <- ggplot(dat, aes(x = xx)) +geom_density(data = subset(dat, yy == 'a'), fill = NA, colour = "#f7746c", alpha = 1) + geom_density(data = subset(dat, yy == 'b'), fill = NA, colour = "#05bdc2", alpha = 1) + xlim(1,8) + labs(x = "rate")

p5 + theme_bw()


n = c(true_rate,cnn_rate)
ggplot(new_dat, aes(new_dat$V2), colour = "red") + geom_density(fill = "red", alpha = 0.2) + xlim(1, 8)



ggplot(new_dat, aes(new_dat$V4)) + geom_density(alpha = 0.1) + xlim(1, 8)


```



