---
title: "Web Aesthetics Linear Regression Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document is about website aesthetics based on 'Predicting Users' First Impressions of Website Aesthetics With a Quantification of Perceived Visual Complexity and Colorfulness' paper's model. The database is based on Intelligent Interactive System Group at Hardward. (url: http://iis.seas.harvard.edu/resources/aesthetics-chi14/)

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r raw_analysis}
library(lme4)
library(lmerTest)

ae6 <- read.csv("C:/Users/z003nefs/Downloads/SupplementaryMaterials/ae_only_unambiguous_1000.csv")

```


In dataset, some data is missing or wrong. Thus, remove and recollect the data in this step
```{r collect}

## change character to factorial number
EducationLevel <- as.factor(ae6$education.x)
Gender <- as.factor((ae6$gender.x))
Agegroup <- ae6$age.x
colorfulnessmodel <- ae6$colorfulnessmodel
complexitymodel <- ae6$complexitymodel
StimulusID  <- ae6$website
ParticipantID <- ae6$participant_id
meanratingaesthetics <- ae6$mean_response


# Gender filter (0, 1, 2 originally, 2 is the uncertain part, change as NA and remove them all)
gen <- Gender
for (i in 1:length(Gender)) {
  if (gen[i] == 2) {
    gen[i] = NA;
  }
}
gen <- as.factor(gen)


# split AgeGroup into 5 levels (<16, 16-25, 25-35, 35-45, > 45)
AgeList <- Agegroup
for (i in 1:length(Agegroup)) {
  if (Agegroup[i] < 16) {
    AgeList[i] = 1
  } else if (Agegroup[i] < 25) {
    AgeList[i] = 2
  } else if (Agegroup[i] < 35) {
    AgeList[i] = 3
  } else if (Agegroup[i] < 45) {
    AgeList[i] = 4
  } else {
    AgeList[i] = 5
  }
}

Agegroup <- as.factor(AgeList)

# rearrnage Educationlevel to 5 levels (pre, high, collge, phd, graduate)
Education <- as.numeric(EducationLevel)
edugroup <- c(1:length(Education))
for (i in 1:length(Education)) {
  if (Education[i]  == 1) {
    edugroup[i] = 1
  } else if (Education[i] == 2) {
   edugroup[i] = 1 
  } else if(Education[i] == 3) {
    edugroup[i] = 2
  } else if (Education[i]== 8) {
    edugroup[i] = 2 
  } else if (Education[i] == 4){
      edugroup[i] = 3
  } else if(Education[i] == 7) {
    edugroup[i] = 5
  } else {
    edugroup[i] = 4
  }
}

edugroup <- as.factor(edugroup)

dat <- data.frame(c1 = meanratingaesthetics, c2 = gen, c3 = edugroup, c4 = Agegroup, c5 = colorfulnessmodel, c6 = complexitymodel, c7 = StimulusID, c8 = ParticipantID)
dat <- na.omit(dat)

meanratingaesthetics <- dat$c1
gen <- as.factor(as.numeric(dat$c2))
edugroup <- dat$c3
Agegroup <- dat$c4
colorfulnessmodel <- dat$c5
complexitymodel <- dat$c6 
StimulusID <- dat$c7
ParticipantID <- dat$c8


```

### Fixed Linear Regression and Analysis

You can also embed plots, for example:

```{r model_analysis}
fixed.lm <-lmer(meanratingaesthetics ~ (gen + edugroup + Agegroup) * (I(colorfulnessmodel^2) + I(complexitymodel^2)) + (1|StimulusID) + (1|ParticipantID), data = dat, REML = FALSE)


# anova
anova(fixed.lm)

# p-value is not default value in lme4 package, then, use 
summary(fixed.lm)

# extract coefficients
coefs <- data.frame(coef(summary(fixed.lm)))

# use normal distribution to approximate p-value
coefs$p.z <- 2* (1-pnorm(abs(coefs$t.value)))
coefs

# check qqplot graph to see the regression
par(mfrow=c(2, 2))
qqplot(edugroup, meanratingaesthetics)
qqplot(Agegroup, meanratingaesthetics)
qqplot(colorfulnessmodel^2, meanratingaesthetics)
qqplot(complexitymodel^2, meanratingaesthetics)

#check regression line
lm.res <- resid(fixed.lm)
par(mfrow=c(1, 1))
plot(lm.res + meanratingaesthetics, meanratingaesthetics, ylab = "real rate", xlab = "lm.model estimate")
abline(1:9, 1:9)

# Pearson's correlation (compare itself)
cor.test(meanratingaesthetics+lm.res, meanratingaesthetics)
```



### Group Analysis
If only consider colorfulness and complexity model, rearrange the dataset

```{r selected_data}



```
